\TheTitle

### 2016-04-25 linvis.tex
minor changes

These methods and visualizations have been implemented in a web-based
tool\footnote{It is currently available at \url{http://li.turingmachine.org}}
instead of the DAG. Our visualizations and tool provide information about the location of any given
commit in the respective merge tree, the files edited, the modules edited, and the
commit message for a given commit or merge. Our tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit ID. The user can request all the
root-level merges containing a commit or merge that matches the query, or all
commits and merges that match the query.

@@

\subsection{Computing the tree-model of the DAG of Linux}

@@

\begin{algorithm}
\caption{Computing the tree-model of Linux Git's DAG}\label{fig:alg}
\begin{algorithmic}
\Function{ComputeTreeModel}{DAG}: tree 
\State {\# Compute the tree from the DAG of a git repository.}
\State {\#  Returns $Tree$, a graph containing every commit }
\State {\# in DAG with the path it followed to master.\\}

@@

>>>>

These methods and visualizations have been implemented in a web-based
tool\footnote{Our visualization tool is currently available at \url{http://li.turingmachine.org}}
instead of the DAG. Our visualizations and tool provide information about the location of any given
commit in the respective merge tree, the files edited, the modules edited, and the
commit message for a given commit or merge. Our tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit ID. The user can request all the
root-level merges containing a commit or merge that matches the query, or all
commits and merges that match the query.

@@

\subsection{Computing the merge-tree of the DAG of Linux}

@@

\begin{algorithm}
\caption{Computing the merge-tree of Linux Git's DAG}\label{fig:alg}
\begin{algorithmic}
\Function{ComputeTreeModel}{DAG}: tree 
\State {\# Compute the tree from the DAG of a git repository.}
\State {\#  Returns $Tree$, a graph containing every commit }
\State {\# in DAG with the path it followed to master.\\}

@@

\dmg{I would remove the command line shell, and use the space for related work}
